---
title: "Regression"
author: "Anna Yeaton"
date: "Fall 2019"
output:
  html_document:
    df_print: paged
fontsize: 11pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = T)
```

# Lab Section

In this lab, we will go over regression. We will be using the caret package in R. https://topepo.github.io/caret/train-models-by-tag.html

# Perfomance Metrics 

## Residual 

Deviation of the observed value to the estimated value (sample mean)
$$residual=y_i - \hat{y_i}$$
where $\hat{y_i}$ is the estimated value

## Mean Squared Error (MSE)

$$MSE=\frac{1}{n}\sum_{i=1}^{n}(y_i - \hat{y_i})^2$$

## Root Mean Squared Error (RMSE)
Same units as original data.

$$RMSE=\sqrt{MSE}$$

## L2 regularization : Ridge regression. Regularize by adding the sum of the coefficients, squared, to the function. 

$$Ridge Regression=\sum_{i=1}^{n}(y_i - w_0 - \sum_{j=1}^{p}w_jx_{ij})^2 + \lambda\sum_{j=1}^p(w_j)^2$$

## L1 regularization : Lasso Regression. Regularize by adding the sum of the absolute value of the coefficients to the model. Coefficient estimates may be pushed to zero -- Lasso can perform variable selection

$$Lasso Regression=\sum_{i=1}^{n}(y_i - w_0 - \sum_{j=1}^{p}w_jx_{ij})^2 + \lambda\sum_{j=1}^p|w_j|$$


\newpage

### The broad steps of Machine learning in R. 

1. Split the data into training and test. Set test aside. 

2. Fit a good model to the training data. 

3. See how your model did on the training data.

4. Test how your model performs on the test data. 

# Regression

```{r, include=FALSE}
library(caret)
library(MASS)
library(ggplot2)
library(dplyr)
library(ggfortify)

#Mauna Loa CO2 concentrations
data(airquality)

```


1. Split data into training and test set (75% in train set, 25% in test set)

```{r}
dt = sort(sample(nrow(airquality), nrow(airquality)*.75))
train_regression = airquality[dt,] 
test_regression = airquality[-dt,]
#train_regression
```


### Linear Regression

* Assumes a linear relationship. 
* Independent variables should not be correlated (no mulitcollinearity)
* The number of observations should be greater than the number of independent variables.


$$RSS=\sum(y_i - \hat{y_i})^2$$
We will predict the response of the Temperature based on Wind. 

This is the data we will fit a linear model to. 
```{r}
 ggplot(data = train_regression) +
   geom_point(aes(x=Wind, y=Temp)) +
   theme_bw()
```

2. Create and fit a linear model to predict Temperature from Wind using the training set

```{r}
#help(train)
lin_co <- 
linear_regression <- train(Temp ~ Wind, data= train_regression , method = "lm")

```


3. Vizualize how your model performed on the train data by plotting the regression line on top of the train data points. 
```{r}
lin_co <- linear_regression$finalModel$coefficients
ggplot(data = train_regression) +
   geom_point(aes(x=Wind, y=Temp)) +
   geom_abline(aes(intercept = lin_co[1], slope = lin_co[2]), col = "blue")+
   theme_bw()
```


4. Explore how the model performs on the test data. For Linear Regression:

* The residuals should be close to zero.
* There should be equal variance around the regression line (homoscedasticity).
* Residuals should be normally distributed.
* Independent variables and residuals should not be correlated.

4 a) See how the model performs on the test data
```{r}
#help(predict)
linear_predict <- predict(linear_regression, test_regression)
linear_predict
```

4 b) Look at the residuals. Are they close to zero?
```{r}
#look at the median residual value. Close to zero is best
#help(summary)
summary(linear_regression)
```


4 c) Plot predicted temperature vs observed temperature. A strong model should show a strong correlation
```{r}
actual_pred <- data.frame(cbind(actual=test_regression$Temp, predicted=linear_predict))  
correlation_accuracy <- cor(actual_pred)

plot(actual_pred$actual, actual_pred$predicted, xlab = "Actual Temp", ylab = "Predicted Temp")
```

4 d) Visualize the predicted values in relation to the real data points. Look for homoscedasticity
```{r}
# Extract coefficients from the model
lin_co <- linear_regression$finalModel$coefficients
lin_co

# plot the regression line on the predicted values
ggplot(data = test_regression) +
   geom_point(aes(x=Wind, y=actual_pred$predicted)) +
   geom_abline(aes(intercept = lin_co[1], slope = lin_co[2]), col = "blue")+
   theme_bw()+ ylab("Predicted Temp")
  

# plot the original test values
ggplot(data = test_regression, aes(x = Wind, y = Temp)) +
  geom_segment(aes(xend = Wind, yend = actual_pred$predicted), alpha = .2) +     
  geom_point(aes(color = "blue")) +  
  guides(color = FALSE, size = FALSE) +                            
  geom_point(aes(y = actual_pred$predicted, col = "red")) +
  theme_bw()
```

4 e) Residuals should be normally distributed. Plot the density of the residuals
```{r}
residuals_lin <- residuals(linear_regression)

ggplot() + geom_density(aes(residuals_lin, col = "red", fill = "red"), show.legend = FALSE) + xlab('residuals')
```


4 f) Independent variables and residuals should not be correlated
```{r}
cor.test(train_regression$Wind, resid(linear_regression))
```


### Linear Regression with Regularization

5. Create a linear model using L1 or L2 regularization to predict Temperature from Wind and Month variables. Plot your predicted values and the real Y values on the same plot. 
```{r}
lasso_reg <- train(Temp ~ Wind + Month, data = train_regression, method = "lasso")
lass_predict <- predict(lasso_reg, test_regression)
a_p <- data.frame(cbind(actual=test_regression$Temp, predicted=lass_predict)) 

ggplot(data = test_regression) +
   geom_point(aes(x=Wind, y=a_p$predicted)) +
   geom_point(aes(x=Month, y=a_p$actual), col = "red") +
   theme_bw()+ ylab("Temp")

ggplot(data = test_regression) +
   geom_point(aes(x=Month, y=a_p$predicted)) +
   geom_point(aes(x=Month, y=a_p$actual), col = "red") +
   theme_bw()+ ylab("Temp")





```


